---
title: "Homework 1"
author: Jingyi Zhang
output: github_document
---

This is my solution to HW1.

```{r load_package, collapse = TRUE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```


## Problem 1

#### Create a data frame with the specified elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

#### Take the mean of each variable in my data frame.

```{r mean_pull_var, collapse = TRUE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r try_numeric, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert numbers, logical, and character to numeric values but not factor.

```{r covert_logical_vectorm, collapse = TRUE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

I cannot convert logical to factor and multiply the random samply by the result.


## Problem 2

#### A short description of the penguins dataset.

* Here are the names in this dataset: `r names(penguins)`. 
  * The range of bill length (mm) is `r range(penguins$bill_length_mm, na.rm = TRUE)`. 
  * The range of bill depth (mm) is `r range(penguins$bill_depth_mm, na.rm = TRUE)`. 
  * The range of flipper_length (mm) is `r range(penguins$flipper_length_mm, na.rm = TRUE)`. 

* This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The mean of flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`mm.

#### Make a scatter plot of flipper length (mm) and bill length (mm).

```{r yx_scatter}
ggplot(data = penguins) +
  geom_point(
    mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species)
  )
ggsave(file = "hw1_plot.pdf", width = 12, height = 9)
```
